% E. Dunham -- Resume
% Contents Copyright (C) 2014 - 2016, E. Dunham

% LaTeX code for rendering the resume is distributed under the MIT license.
% See LICENSE.txt. It means you can use the code for whatever you want,
% including your own resume, but I'm not liable if it catches your computer on
% fire.

% Template originally developed by E. Dunham
% https://github.com/edunham/resume/blob/master/resume.tex

\documentclass[11pt]{article} % Set default font size to 11pt


% Some settings that the stuff hidden in the preamble will reference
\def \whitespaciness { 0 } % pt. bigger numbers = emptier page. 0 is ok.
\def \typeoffill {\dotfill} % hfill makes blank, dotfill makes dotted lines.


\input{preamble}
\begin{document}

\centerline{{\Huge \bf E. Dunham}}

\bigskip

\contact{resume@edunham.net}
        {edunham.net}
        {github.com/edunham}
        {Remote, Oregon, USA}

\heading{Skills}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\skill{Community}
    {Slack, Discord, IRC collaboration \& administration. Git \& GitHub.}

\skill{Advocacy}
    {Presentations at edunham.net/pages/talks.html}


\skill{Infrastructure}
    {Terraform, K8s, Docker. AWS, GCP, Azure. Chef, Ansible, Puppet.}

\skill{Automation}
    {Python, Bash, Rust, yaml. TravisCI, Jenkins, GitHub Actions}

%\skill{Community}
%      {Teaching, public speaking, event planning, curriculum design}

%\skill{Collaboration}
%      {IRC/Slack, Git \& GitHub, Sphinx, Pandoc, Jira/RT/Bugzilla}

%\skill{Robotics}
%      {Mechanical design \& prototyping, 3D modeling, OpenCV, Arduino}

\heading{Employment}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish

\experience{Okta}
           {Senior Developer Advocate}
           {09/2021 - present}

Present workshops, webinars, panels, podcasts, etc. Extensive cross-team collaboration. 

Educate developers and integration builders on automation, identity protocols, integration network. 

Represent organization at events; assist with organizing events. 

Mentor colleagues within team and across organization in technical and soft skills. 

Interview candidates and assist with hiring. 

\experience{PagerDuty}
           {Senior Site Reliability Engineer}
           {06/2020 - 08/2021}

Python, Chef, AWS, Terraform. Supported and improved essential internal services.  

Coordinated deployment of Delivery team's infrastructure services to new service region.

Maintainer and on-call for critical CI/CD services. Facilitated incident response process within team.

Mentored junior team members and assisted with hiring.

\experience{Mozilla}
           {Operations Engineer}
           {08/2018 - 05/2020}

Primary ops engineer in refactor and migration of Taskcluster build system 
from AWS to GCP. 

Designed and deployed development and production environments for multiple services

\experience{Mozilla Research}
           {DevOps Engineer \& Rust Evangelist}
           {05/2015 - 08/2018}

Improved hosting and continuous integration infrastructure for teams
including Rust, Servo, \& VR.

Maintained BuildBot deployment on Linux, Windows, and OS X hosts (physical and
AWS servers).

Deployed security best practices, including migrating 2 teams to 1password.

Presented over 20 talks on Rust and Servo, including RustFest Kyiv closing keynote.

\experience{Urban Airship}
           {Operations Team Intern}
           {06/2014 - 09/2014}

Migrated services using Chef and Jenkins to facilitate datacenter move.

Led interdisciplinary Hack Week team to develop Flask frontend to internal
LDAP API.

Audited and improved documentation for over 30 internal Java, Go, and Python
services.

\experience{OSU Open Source Lab}
           {Student Systems Administrator}
           {12/2012 - 06/2014}

Solved hardware and software problems for over 100 hosted projects.

% \experience{Intel}
%            {Software Enabling Group USB3 Team Intern}
%            {06/2012 - 09/2012}
% 
% Collaborated using agile development with scrum methodology.
% 
% Prototyped solution to double Android USB3 throughput with Java, C, \CPP.

\end{description}

\heading{Community}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{PDX Rust Users Group}
           {Organizer}
           {2015 - 2017}

Organized monthly meetups, communicated users' feedback to Rust core team.

\experience{Rust Community Team}
           {Volunteer}
           {2016 - 2018}

Represented Rust project at events. Produced \& distributed stickers, plushies, training resources.

\experience{OSU DevOps Bootcamp}
           {Founder}
           {2013 - 2015}

Designed and implemented comprehensive systems engineering curriculum.

Distributed Apache 2.0 licensed curriculum (devopsbootcamp.osuosl.org)

\experience{OSU Linux Users Group}
           {President}
           {2012 - 2014}

Organized weekly meetings, mentored students in FOSS involvement

\end{description}

\heading{Academics}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{description}
\squish
\experience{Oregon State University}
           {}
           {2010-2015}

Upper-division coursework in Computer Science including Operating Systems,\\
Software Engineering, Analysis of Algorithms, Cryptography, and Applied Robotics.

\end{description}


% \heading{Licenses and Qualifications}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{description}
% \squish
% \experience{Oregon Emergency Medical Responder}
%            {License no. 202296}
%            {2018 - Present}
% 
% www.oregon.gov/oha/ph/providerpartnerresources/emstraumasystems/pages/vertification.aspx
% 
% \experience{NWCG S-190}
%            {Introduction to Wildland Fire Behavior}
%            {April 2021}
% \experience{NWCG S-130}
%            {Firefighter Training}
%            {April 2021}
% \experience{NWCG L-180}
%            {Human Factors in the Wildland Fire Service}
%            {April 2021}
% 
% Certificates of completion available upon request
% 
% \end{description}




%\heading{Recent Speaking Engagements}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\squish
%
%\event{Linux.conf.au}
%      {01/2018}
%      {}
%      {Should you rewrite in Rust?}
%
%\event{GitHub Universe}
%      {10/2017}
%      {}
%      {Building a better browser engine on GitHub}
%
%\event{RustFest Kyiv}
%      {04/2017}
%      {Keynote lecture}
%      {Spreading Rust}
%
%\hfill \small ...and more at https://edunham.net/pages/talks.html

\end{document}
